\pkg{DNest4}: Diffusive Nested Sampling in \proglang{C++} and \proglang{Python}

### 2016-12-08 paper/ms.tex
url

Development of \pkg{DNest4} takes place in the \pkg{git} repository located at
\begin{center}
{\tt https://github.com/eggplantbren/DNest4/}\\
\end{center}
The software
is licensed under the permissive open source
MIT license. To compile and run \pkg{DNest4},
you require a recent version of the GNU
\proglang{C++} compiler, \pkg{g++} \citep{gcc}.
\pkg{DNest4} uses features from the \proglang{C++11} standard
\citep{c++11}.

The \proglang{Python}
packages \pkg{NumPy} \citep{numpy}, \pkg{matplotlib} \citep{matplotlib},
and \pkg{Cython} \citep{cython} are also needed.
To download and compile \pkg{DNest4}
the following steps are sufficient:
\begin{CodeChunk}
\begin{CodeInput}
> wget https://github.com/eggplantbren/DNest4/archive/0.1.3.tar.gz
> tar xvzf 0.1.3.tar.gz
> mv DNest4-0.1.3 DNest4
> cd DNest4/code
> make
> cd ../python
> python setup.py install
\end{CodeInput}
\end{CodeChunk}

@@

\begin{figure}[ht!]
\begin{center}
\hspace*{-2cm}\includegraphics[width=0.4\textwidth]{figures/rjobject_pgm.pdf}
\caption{A PGM showing the kind of prior information the \code{RJObject}
template class expresses.
Figure created using Daft ({\tt http://daft-pgm.org}).\label{fig:rjobject_pgm}}
\end{center}
\end{figure}

>>>>

Development of \pkg{DNest4} takes place in the \pkg{git} repository located at
\begin{center}
\url{https://github.com/eggplantbren/DNest4/}
\end{center}
The software
is licensed under the permissive open source
MIT license. To compile and run \pkg{DNest4},
you require a recent version of the GNU
\proglang{C++} compiler, \pkg{g++} \citep{gcc}.
\pkg{DNest4} uses features from the \proglang{C++11} standard
\citep{c++11}.

The \proglang{Python}
packages \pkg{NumPy} \citep{numpy}, \pkg{matplotlib} \citep{matplotlib},
and \pkg{Cython} \citep{cython} are also needed.
To download and compile \pkg{DNest4}
the following steps are sufficient:
\begin{CodeChunk}
\begin{CodeInput}
> wget https://github.com/eggplantbren/DNest4/archive/0.1.4.tar.gz
> tar xvzf 0.1.4.tar.gz
> mv DNest4-0.1.4 DNest4
> cd DNest4/code
> make
> cd ../python
> python setup.py install
\end{CodeInput}
\end{CodeChunk}

@@

\begin{figure}[ht!]
\begin{center}
\hspace*{-2cm}\includegraphics[width=0.4\textwidth]{figures/rjobject_pgm.pdf}
\caption{A PGM showing the kind of prior information the \code{RJObject}
template class expresses.
Figure created using Daft (\url{http://daft-pgm.org}).\label{fig:rjobject_pgm}}
\end{center}
\end{figure}
